A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-07-26 draft/paper2_v3.tex
Edit data and sample 2

    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out surrounding neighbors and accounting for the subtraction of the background light. We use the broadband spectral energy distributions (SED) fitting code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. We assume a Chabrier IMF \citep{Chabrier2003}, the Flexible Stellar Population 
    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), a Calzetti extinction law \citep{Calzetti2000}, and a simple delayed-$\tau$ model for star 
    formation histories (SFH). Using HSC data, we can measure the mass profiles of massive galaxies to $\sim 100$ kpc and we integrate these profiles within isophotal elliptical apertures at different physical radii. As explained in Paper I, here focus on the two following metric masses:

@@

        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use as a proxy for the 
            \textit{in situ} stellar component. This is motivated both by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). The value of 10 kpc that we quote here corresponds to the radius of the major axis of the isophotal ellipse (xxx check).
        \item stellar mass within 100 kpc (hereafter noted \mtot{}). We use \mtot{} as a proxy of the total stellar mass. In Paper I we showed that \mtot{} recovers more light compared to HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex in magnitude.           
   \end{itemize}

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full redshift range. In addition to the mass cut above, we also limit our sample to galaxies that live at the centers of their own 
    dark matter haloes-- so-called ``central'' galaxies. We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog to construct a central galaxy sample.

    %Central galaxies are important to the study of galaxy-halo connection and follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.

    Firstly, we select 68 massive central galaxies from \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
    at the high end of our redshift window. The $P_{\mathrm{Cen}}$ limit is 
    selected to exclude low probability central galaxy candidates. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these corresponds to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2016}. 
    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
    \citet{Diemer2015}. We further exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the photometric 
    redshift uncertainty of the cluster (typically around 0.015 to 0.025). This second sample will be dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. There are  833 galaxies with  
\logmtot{}$> 11.6$ in this sample.

@@

    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
    \minn{} for the \rbcg{} and \nbcg{} samples. 
    We also compare these two samples on the \mtot{} - rest-frame $g-r$ color plane. 
    Both of them follow the same ``red-sequence'' with only a handful of galaxies displaying bluer colors.

>>>>

    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out surrounding neighbors and accounting for the subtraction of the 
    background light. 
    We use the broadband spectral energy distributions (SED) fitting code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using 
    five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. 
    We assume a \citet{Chabrier2003} IMF, the Flexible Stellar Population 
    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), the 
    \citet{Calzetti2000} extinction law, and a simple delayed-$\tau$ model for 
    star formation histories (SFH). 
    Using HSC data, we can measure the \mden{} profiles of massive galaxies to 
    $\sim 100$ kpc and we integrate these profiles within elliptical isophotal
    apertures at different physical radii. 
    As explained in Paper~I, here we focus on the two following metric masses:

@@

        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use 
            as a proxy for the stellar mass of the \textit{in situ} stellar 
            component. 
            This is motivated both by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). 
            The value of 10 kpc that we quote here corresponds to the radius of the 
            major axis of the isophotal ellipse.

        \item stellar mass within 100 kpc (hereafter noted \mtot{}). 
            We use \mtot{} as a proxy of the ``total'' stellar mass. 
            In Paper~I we showed that \mtot{} recovers more light compared to 
            HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex 
            in magnitude.

   \end{itemize}

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
    to help us construct a central galaxy sample.

    %Central galaxies are important to the study of galaxy-halo connection and follow 
    %stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.

    Firstly, we select 68 massive central galaxies from \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
    central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    correspond to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2016}. 
    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
    \citet{Diemer2015}. 
    We further exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
    This second sample will be dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. \
    There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.

@@

    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
    \minn{} for the \rbcg{} and \nbcg{} samples. 
    We also compare these two samples on the \mtot{}--rest frame $g-r$ color plane. 
    Both of them follow the same ``red-sequence'' with only a handful of galaxies 
    displaying bluer colors.
